---
title: "Group_assignment"
author: "Marc Zeng"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
hist_data <- read.csv('hist_data.csv')
dataA1 = read.csv("dataA1.csv")
dataB1 = read.csv("dataB1.csv")
dataA2_or = read.csv("dataA3.csv")
dataB2_or = read.csv("dataB2.csv")
dataA3_or = read.csv('dataA3.csv')
dataB3_or = read.csv('dataB3.csv')
dataA4_or = read.csv('dataA4.csv')
dataB4_or = read.csv('dataB4.csv')

dataA2 = rbind(dataA1, dataA2_or)
dataB2 = rbind(dataB1, dataB2_or)
dataA3 = rbind(dataA2, dataA3_or)
dataB3 = rbind(dataB2, dataB3_or)
dataA4 = rbind(dataA3, dataA4_or)
dataB4 = rbind(dataB3, dataB4_or)

```

**Case Summary** Case objective: To examinate whether the proposal of
decreasing rank tolerance parameter to 4 points and increasing the
cut-off parameter to 20 seconds could improve the revenue.

Background information: The company creates revenue by in-game virtual
item purchase and ad clicks. The longer time the play is, the more
likely the virtual items would be purchased. The longer time the idle
time is, the more ad are likely to be clicked. Players with closer rank
could longer the playing time. Playing with bot only spends short time.
On average, each ad click could result in \$0.01 income and in-game
virtual item purchase values between \$1 to \$5. The original matching
algorithm is that the rank tolerance is 5 points and cut-off time is 15
second. The new proposed one is that the rank tolerance is 4 points and
cut-off time is 20 seconds. Supposedly, renuvue from both ad clicks and
in-game virtual item purchase would be increased.

Key stakeholder concerns: As the new proposal is under test, if the
revenue is decreasing rather than increasing as expected, the potential
loss would be huge. Also, longer idle time could undermine the user
experience, which brings potential customer loss risk.

Decision point: After A/B test, if the revenue could be proved to show
significant increase, the new proposal could be adopted, or the original
one would be kept.

**A/B Test Design** Hypotheses: H0: The new proposal has no significant
effect on revenue (revenue regarding new proposal \<= revenue regarding
original algorithm). H1: The new proposal increases revenue (revenue
regarding new proposal \> revenue regarding original algorithm).

HO: The new proposal has no significant effect on more ads clicked
during idle time (\<=) H1: (\>)

H0: The new proposal has no significant effect on increase of game
duration. (\<=) H1: (\>)

H0: The new proposal has no significant effect on increase of in-game
purchases. (\<=). H1: (\>)

Randomization plan: Not required for now.

Data Collection plan: From quercus

Statistical testing method: As the data is collected with time
sequentially ,the SPRT method could be adopted. Note that in order to
control Type I error and control power of the test, alpha is set to be
0.05 and beta is set to be 0.2.

**A/B Test** Day One A1/B1
```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
    # Compute average revenue from ads and in-game purchases for control group
avg_ad_revenue_A1<- mean(dataA1$ad_clicks)*0.01
avg_purchase_revenue_A1 <- mean(dataA1$in_game_purchases)
# Compute average revenue from ads and in-game purchases for treatment group
avg_ad_revenue_B1 <- mean(dataB1$ad_clicks) * 0.01
avg_purchase_revenue_B1 <- mean(dataB1$in_game_purchases)

# T-test for total revenue
t_test_total_revenue_day1 <- t.test(dataA1$ad_clicks * 0.01+dataA1$in_game_purchases,
                                    dataB1$ad_clicks * 0.01+dataB1$in_game_purchases)
t_test_total_revenue_day1$p.value

# T-test for ad revenue
t_test_ad_revenue_day1 <- t.test(dataA1$ad_clicks*0.01, dataB1$ad_clicks*0.01)
t_test_ad_revenue_day1$p.value

# T-test for in-game purchase revenue
t_test_purchase_revenue_day1 <- t.test(dataA1$in_game_purchases, dataB1$in_game_purchases)
t_test_purchase_revenue_day1$p.value
#
t_test_gduration_day1 <- t.test(dataA1$play_time, dataB1$play_time)
t_test_gduration_day1$p.value


```



Day Two A2/B2

```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
avg_ad_revenue_A2 <- mean(dataA2$ad_clicks)*0.01
avg_purchase_revenue_A2 <- mean(dataA2$in_game_purchases)
# Compute average revenue from ads and in-game purchases for treatment group
avg_ad_revenue_B2 <- mean(dataB2$ad_clicks) * 0.01
avg_purchase_revenue_B2 <- mean(dataB2$in_game_purchases)

# T-test for total revenue
t_test_total_revenue_day2 <- t.test(dataA2$ad_clicks * 0.01+dataA2$in_game_purchases,
                                    dataB2$ad_clicks * 0.01+dataB2$in_game_purchases)
t_test_total_revenue_day2$p.value

# T-test for ad revenue
t_test_ad_revenue_day2 <- t.test(dataA2$ad_clicks*0.01, dataB2$ad_clicks*0.01)
t_test_ad_revenue_day2$p.value

# T-test for in-game purchase revenue
t_test_purchase_revenue_day2 <- t.test(dataA2$in_game_purchases, dataB2$in_game_purchases)
t_test_purchase_revenue_day2$p.value

t_test_gduration_day2 <- t.test(dataA2$play_time, dataB2$play_time)
t_test_gduration_day2$p.value
```



For chances of matching players with closer ranks

```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
# T-test for total reveue
t_test_total_revenue_day3 <- t.test(dataA3$ad_clicks*0.01+dataA3$in_game_purchases,dataB3$ad_clicks * 0.01+dataB3$in_game_purchases)
t_test_total_revenue_day3$p.value

# T-test for ad revenue
t_test_ad_revenue_day3 <- t.test(dataA3$ad_clicks * 0.01, dataB3$ad_clicks * 0.01)
t_test_ad_revenue_day3$p.value

# T-test for in-game purchase revenue
t_test_purchase_revenue_day3 <- t.test(dataA3$in_game_purchases, dataB3$in_game_purchases)
t_test_purchase_revenue_day3$p.value

t_test_gduration_day3 <- t.test(dataA3$play_time, dataB3$play_time)
t_test_gduration_day3$p.value


```

So, in day 3, total revenue and in-game purchase and game duration demonstrated
significant change already.
Test the power


```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
K <- 1000
rej <- rep(NA,K)
n = length(dataA3$in_game_purchases)
x <- dataA3$in_game_purchases * 0.01
y <- dataB3$in_game_purchases * 0.01
for(i in 1:K){
  ind <- sample(1:n,size=n,replace=TRUE)
  rej[i] <- t.test(x[ind],y[ind])$p.value<0.05
}

ttestPow <- sum(rej)/K
ttestPow
```

```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
K <- 1000
rej <- rep(NA,K)

n = length(dataA3$play_time)
x <- dataA3$play_time
y <- dataB3$play_time
for(i in 1:K){
  ind <- sample(1:n,size=n,replace=TRUE)
  rej[i] <- t.test(x[ind],y[ind])$p.value<0.05
}

ttestPow <- sum(rej)/K
ttestPow
```

```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
total_revenueA3 <- dataA3$ad_clicks * 0.01+dataA3$in_game_purchases
total_revenueB3 <- dataB3$ad_clicks * 0.01+dataB3$in_game_purchases
K <- 1000
rej <- rep(NA,K)
n = length(total_revenueA3)
x <- total_revenueA3 
y <- total_revenueB3
for(i in 1:K){
  ind <- sample(1:n,size=n,replace=TRUE)
  rej[i] <- t.test(x[ind],y[ind])$p.value<0.05
}

ttestPow <- sum(rej)/K
ttestPow
```



So, in day 3, total revenue and in-game purchase and game duration demonstrated
significant change already.
Test the power


```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
dataA4 = rbind( dataA1, dataA2, dataA3)
dataB4 = rbind(dataB1, dataB2, dataB3)

# T-test for ad revenue
t_test_ad_revenue_day4 <- t.test(dataA4$ad_clicks * 0.01, dataB4$ad_clicks * 0.01)
t_test_ad_revenue_day4$p.value


```


```{r, results='hide', echo=FALSE}
# Simulated p-values from four hypothesis tests
p_values <- c(0.003884644, 0.003887117, 0.0005561706)

# Set the original significance level (alpha)
alpha <- 0.05

# Number of tests conducted
m <- length(p_values)

# Calculate the Bonferroni-corrected significance level
alpha_bonferroni <- alpha / m

# Create a vector to store adjusted results
adjusted_results <- vector("logical", length = m)

# Apply the Bonferroni correction
for (i in 1:m) {
  adjusted_results[i] <- p_values[i] <= alpha_bonferroni
}

# Print the Bonferroni-corrected results

cat("Bonferroni-corrected results (Significant if TRUE):\n", adjusted_results, "\n\n")
cat("Bonferroni-corrected significance level (Alpha Bonferroni):\n", alpha_bonferroni, "\n")

```








